\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-12 submission/root.tex

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
%\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
\usepackage{mathtools}   % loads »amsmath«
\usepackage{amssymb,amsmath}
\usepackage{amsfonts}
\usepackage{color}

@@

\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory S. Chirikjian$^{2}$% <-this % stops a space
\thanks{*This work \textcolor{blue}{was} %is 
partially
supported by NSF Grant RI-Medium: \textcolor{blue}{1162095}}%\#IIS-1162095}% <-this % stops a space
\thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University, Beijing 100191, China
        {\tt\small haiyuanli@hotmail.com}, {\tt\small itm@buaa.edu.cn}}%
\thanks{$^{2}$Qianli Ma and Gregory S. Chirikjian \textcolor{red}{are} with the Department of Mechanical Engineering, Johns Hopkins University,
        Baltimore, MD 21218, USA
        {\tt\small mqianli1@jhu.edu}, {\tt\small gregc@jhu.edu}}%
}

@@

%In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem. Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams. A probabilistic method is presented to solve the homogeneous matrix equations without a priori knowledge of the correspondence. Using the Euclidean-Group invariants, an exact solution can be found. For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
\textcolor{blue}{Calibration is often an important and necessary step in the use of image-guided systems. In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control. As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony is sampling rates and processing time. One common scenario is a constant shift between the two data streams. Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$s and $B$s. We begin by discussing probability density functions on $SE(3)$ and then introduce Euclidean-group invariants to obtain an exact solution for $X$ and $Y$. Then, we present a method to simultaneously recover $X$ and $Y$ and the correspondence between the shifted data sets. Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness. }

@@

Image-guided systems have been widely %used
\textcolor{blue}{employed in applications throughout} %in 
robotics such as robot\textbf{\textcolor{blue}{-}}assisted surgery, %automatic
\textcolor{blue}{autonomously} guided vehicle\textcolor{blue}{s}, etc. Sensors such as a camera, a laser scanner\textbf{\textcolor{blue}{,}} or an ultrasound probe are usually mounted on the distal end of a robotic manipulator. For a typical ``hand-eye'' system as described above, the relative transformation %of 
\textcolor{blue}{between} the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well\textbf{\textcolor{blue}{-}}known $\textbf{AX=XB}$ problem. A variation of this problem is the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated. In a typical environment, % setup, 
the relationships %among
\textcolor{blue}{between} the sensor frame, robot frame\textcolor{blue}{,} and world frame are variant and %the
 uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robot%s
  to respond to dynamic environments.

In the $\textbf{AX=YB}$ problem, data streams \textcolor{blue}{of} $A$s and $B$s can be respectively obtained via different sensors. The data streams %can be in
\textcolor{blue}{may arrive in} an asynchronous fashion due to the different working frequencies of the sensors. \textcolor{blue}{This} %The 
asynchrony causes a shift between the two \textcolor{blue}{data} streams %of data
which \textcolor{blue}{removes} %damages 
the correspondence between \textcolor{blue}{the} $A$s and $B$s. In this paper, a novel method is presented to solve for $X$ and $Y$ without %the need to know 
a priori knowledge of the correspondence between \textcolor{blue}{the} $A$s and $B$s.

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem %which is 
formulated as AX=YB. (2) The hand-eye calibration problem %which is 
formulated as AX=XB. (The Universal Robot \textcolor{blue}{pictured above} %as Shown in the Picture 
is owned by Prof. Emad Boctor \textcolor{blue}{of} %in the 
Johns Hopkins University). 
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), {\color{red}$A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$}. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ %is
\textcolor{blue}{are} the relative transformations obtained from the raw data), many \textcolor{blue}{deterministic} methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. All of the methods above assume a prior\textcolor{blue}{i} knowledge of \textcolor{blue}{the} exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without \textcolor{blue}{a priori knowledge of the} correspondence. These %s
  methods assume that there \textcolor{blue}{are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown}% is exact knowledge of the correspondence between $\{A_i\}$ and $\{B_i\}$
   \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Simulatneous calibration %s 
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why \textcolor{blue}{a} simultaneous solution for $X$ and $Y$ in \textcolor{blue}{the} $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot \textcolor{blue}{transformations}, %system,
 and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a prior\textcolor{blue}{i}. In this paper, we focus on one case of \textcolor{blue}{the} $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

The rest of the paper is organized as follows. {\color{red}In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$.} In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, {\color{red} which is used to select the optimal solution among the candidates}. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. Finally, conclusions are drawn based on the numerical results and possible future work \textcolor{blue}{is} %s are
pointed out.

\section{Solving AX=YB using a probabilistic method on motion groups}
\label{sect2}
In this section, a brief introduction to the concept %s
 of probability density function\textcolor{blue}{s (PDFs)} on the special Euclidean group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ \textcolor{blue}{is} %are
  derived.

Any rigid \textcolor{blue}{body} transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for \textcolor{blue}{the} group element.

@@

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK.
\end{equation}
where $\circ$ denotes the group product, and in this case it is simply matrix multiplication.
Employing the properties of \textcolor{blue}{the} $\delta$ function, it is straightforward to see that:

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}

Defin\textcolor{blue}{ing} %e 
the \textcolor{blue}{PDF} %probability density function 
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
\end{IEEEeqnarray}
\textcolor{blue}{then by using the distributivity of convolution, adding $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ8}), and substituting Eq.\textcolor{blue}{~}(\ref{equ7}) in, we have:}
%Using the distributivity of convolution, add $n$ instances of Eq.(\ref{equ8}) and substitute Eq.(\ref{equ7}) in, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(\textcolor{blue}{H})=(\delta_{Y}\ast f_{B_{i}})(\textcolor{blue}{H})
%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

@@

If each of the data stream\textcolor{blue}{s} $\{A_i\}$ and $\{B_i\}$ \textcolor{blue}{are} %is 
generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly\textbf{\textcolor{blue}{-}}focused''. The convolution of two highly\textbf{\textcolor{blue}{-}}focused \textcolor{blue}{PDFs} %probability density functions (PDF) 
have some interesting properties that can be used to solve for $X$. 
For simplicity, we will drop the integral interval ``$SE(3)$'' for the \textcolor{blue}{remainder of the paper}, 
%rest of equations, 
\textcolor{blue}{as} %and 
it should be self-\textcolor{blue}{evident} %clear 
given the integration \textcolor{blue}{measure} %variable 
that is used. %In particular, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ $f(H)$ as:
\textcolor{blue}{In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:}

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
If $f_A(H)$ is given as in Eq.\textcolor{blue}{~}(\ref{equ8}), then \textcolor{blue}{the} %its
 corresponding discrete version of \textcolor{blue}{the} mean $M_A$ and covariance $\Sigma_A$ will be:

@@

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly\textbf{\textcolor{blue}{-}}focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:

@@

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively. Therefore, the following equations can be obtained using Eq.\textcolor{blue}{~}(\ref{equ14}):

@@

To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as \textcolor{blue}{follows:}%below:

@@

\begin{equation}\label{equ18}
    \Lambda = (Q_{M_{A}}^{T}R_{X}^{T}Q_{M_{B}}) \Lambda (Q_{M_{B}}^{T}R_{X}Q_{M_{A}})= P \Lambda P^{T}
\end{equation}
where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, then a rotation matrix $P$ that satisfies Eq.\textcolor{blue}{~}(\ref{equ18}) can be one of $\mathcal{P}$ or $\mathcal{-P}$ :

@@

Therefore, there are eight candidates \textcolor{blue}{for} %of 
$R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained from Eq.\textcolor{blue}{~}(\ref{equ17b}). Given known $X$, $Y$  can be solved \textcolor{blue}{from} %for by 
\textcolor{blue}{$Y = M_AXM_B^{-1}$.} %$Y = M_A^{-1}XM_B^{-1}$.
 At last, eight candidate pairs of  $\{X_{k},Y_{k}\}$ can be obtained as:

@@

The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
Based on %the
 screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:

@@

Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$. Defin\textcolor{blue}{ing} %e
 $B^k = X_k^{-1}Y_kB$, %and 
 we %will
  have $AX_k=X_kB^k$. There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:

@@

\begin{equation}\label{equ23}
    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{k},Y_{k})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
\end{equation}
Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$ \textcolor{blue}{to be known}. However,
the correspondences need %s
 to be recovered to pick the optimal $(X_k, Y_k)$.
\section{Solution with unknown correspondence between $A_{i}$ and $B_{j}^{k}$}
\label{sect3}

In most cases, the two sets of homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors. Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$ is usually unknown. This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-%G
\textcolor{blue}{g}roup invariants are used to recover the correspondence between the data streams. The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is no %t 
a priori knowledge of the correspondence. However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-%G
\textcolor{blue}{g}roup invariants, it is straightforward to determine which \textcolor{blue}{is the optimal pair} %pair is the optimal one 
if the correspondence between $A_{i}$ and $B_{j}^{k}$ can be known.

@@

The discrete convolution of two sequences $f_{n}$ and $g_{n}$ \textcolor{blue}{is} %are 
defined \textcolor{blue}{as:}

\begin{equation}\label{equ26}
	\textcolor{blue}{(f \ast g)(\tau)=\sum_{j=0}^{N}f(t_{j})g(t_{j}-\tau).}
	% Since you are using i for imaginary numbers use j here instead
    %(f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
\end{equation}

@@

\begin{equation}\label{equ28}
    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot \textcolor{blue}{\mathcal{F^{*}}(g)].}%(\mathcal{F}(g))^{*}].
\end{equation}

>>>>

%\usepackage{amsmath}   % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
\usepackage{multirow}
%\usepackage[left=0.71in,top=0.94in,right=0.71in,bottom=1.18in]{geometry}
%\setlength{\columnsep}{0.24in}
% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}
\usepackage{mathtools}   % loads Â»amsmathÂ«
\usepackage{amssymb,amsmath}
\usepackage{amsfonts}
\usepackage{color}

@@

\author{Haiyuan Li$^{1}$, Qianli Ma$^{2}$, Tianmiao Wang$^{1}$ and Gregory S. Chirikjian$^{2}$% <-this % stops a space
\thanks{*This work was partially supported by NSF Grant RI-Medium: 1162095. Mr. Haiyuan Li's partial work is supported by ¡°863¡± Program
of China: 2012AA041402.}%% <-this % stops a space
\thanks{$^{1}$Haiyuan Li and Tianmiao Wang are with the School of Mechanical Engineering and Automation, Beihang University, Beijing 100191, China
        {\tt\small haiyuanli@hotmail.com}, {\tt\small itm@buaa.edu.cn}}%
\thanks{$^{2}$Qianli Ma and Gregory S. Chirikjian are with the Department of Mechanical Engineering, Johns Hopkins University,
        Baltimore, MD 21218, USA
        {\tt\small mqianli1@jhu.edu}, {\tt\small gregc@jhu.edu}}%
}

@@

%In image-guided systems, the relative transformations of hand-eye ($X$) and robot-world ($Y$) coordinates have to be calculated and a simultaneous solution is useful in sensor calibration problem. Due to the asynchrony of sensors' timing, the exact correspondence between $A$ and $B$ is unknown, and a common scenario is when there is a constant shift between the two data streams. A probabilistic method is presented to solve the homogeneous matrix equations without a priori knowledge of the correspondence. Using the Euclidean-Group invariants, an exact solution can be found. For noisy and shifted data streams, we numerically simulated the proposed method, and the results show the efficiency and robustness.
Calibration is often an important and necessary step in the use of image-guided systems. In the case of the $AX=YB$ problem, the relative hand-eye ($X$) and robot-world ($Y$) transformations must be determined to provide accurate data for use in control. As an added difficulty, the exact correspondence between the streams of sensor data ($A$s and $B$s) is typically unknown due to asynchrony in sampling rates and processing time. One common scenario is a constant shift between the two data streams. Therefore, in this paper we present a probabilistic method to simultaneously solve for $X$ and $Y$ without a priori knowledge of the correspondence between the streams of $A$s and $B$s. We begin by discussing probability density functions on $SE(3)$ and then introduce Euclidean-group invariants to obtain an exact solution for $X$ and $Y$. Then, we present a method to simultaneously recover $X$ and $Y$ and the correspondence between the shifted data sets. Finally, we numerically simulated the proposed method with shifted, asynchronous data and noise added to the stream of $B$s to verify its efficiency and robustness.

@@

Image-guided systems have been widely employed in applications throughout robotics such as robot-assisted surgery, autonomously guided vehicles, etc. Sensors such as a camera, a laser scanner, or an ultrasound probe are usually mounted on the distal end of a robotic manipulator. For a typical ``hand-eye'' system as described above, the relative transformation
between the sensor with respect to the end-effector should be accurately calibrated, and it is often characterized as the well-known $\textbf{AX=XB}$ problem. A variation of this problem is the $\textbf{AX=YB}$ problem, where both the hand-eye transformation and the pose of the robot base with respect to the world frame need to be calibrated. In a typical environment, the relationships between the sensor frame, robot frame, and world frame are variant and uncertainties exist. Therefore, simultaneous coordinate calibrations have to be determined frequently in order to enable the robot to respond to dynamic environments.

In the $\textbf{AX=YB}$ problem, data streams of $A$s and $B$s can be respectively obtained via different sensors. The data streams may arrive in an asynchronous fashion due to the different working frequencies of the sensors. This asynchrony causes a shift between the two data streams which removes the correspondence between the $A$s and $B$s. In this paper, a novel method is presented to solve for $X$ and $Y$ without a priori knowledge of the correspondence between the $A$s and $B$s.

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem formulated as AX=YB. (2) The hand-eye calibration problem formulated as AX=XB. Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems. (The Universal Robot pictured above is owned by Prof. Emad Boctor of Johns Hopkins University).
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Simulatneous calibration %s
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a priori. In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

The rest of the paper is organized as follows. In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$. In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.

\section{Solving AX=YB using a probabilistic method on motion groups}
\label{sect2}
In this section, a brief introduction to the concept %s
 of probability density functions (PDFs) on the special Euclidean group $SE(3)$ is presented and the probabilistic representation of $AX=YB$ is derived.

Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector and $H$ is the symbol for the group element.

@@

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}\circ H)dK.
\end{equation}
where $\circ$ denotes the group product, and in this case it is simply matrix multiplication. Employing the properties of the $\delta$ function, it is straightforward to see that:

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}
Defing the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

@@

If each of the data streams $\{A_i\}$ and $\{B_i\}$ are generated using Gaussian distribution over $SE(3)$, then they can be viewed as ``highly-focused''. The convolution of two highly-focused PDFs have some interesting properties that can be used to solve for $X$.
For simplicity, we will drop the integral interval ``$SE(3)$'' for the remainder of the paper, as it should be self-evident given the integration measure that is used. In particular, the mean $M$ and covariance $\Sigma$ of a PDF $f(H)$ on $SE(3)$ are defined as:

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
If $f_A(H)$ is given as in Eq.~\ref{equ8}, then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:

@@

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:

@@

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively. Therefore, the following equations can be obtained using Eq.~\ref{equ14}:

@@

To solve the above equations, Eq.\textcolor{blue}{~}(\ref{equ15a}) is decomposed into a rotational equation and a translational equation as follows:

@@

\begin{equation}\label{equ18}
    \Lambda = (Q_{M_{A}}^{T}R_{X}^{T}Q_{M_{B}}) \Lambda (Q_{M_{B}}^{T}R_{X}Q_{M_{A}})= P \Lambda P^{T}
\end{equation}
where $P=Q_{M_{A}}^{T}R_{X}Q_{M_{B}}$. If $Q_{M_{A}}$ and $Q_{M_{B}}$ are further constrained to be rotation matrices, the rotation matrix $P$ satisfies Eq.\textcolor{blue}{~}(\ref{equ_P}).

\begin{equation}\label{equ_P}
\left\{
\begin{array}{l}
P^{T} = P^{-1} \\
det(P) = \pm 1.
\end{array}
\right.
\end{equation}
Combing Eq.~(\ref{equ18}) and Eq.~(\ref{equ_P}), then a rotation matrix $P$ can be one of $\mathcal{P}$ or $\mathcal{-P}$ :

@@

Therefore, there are eight candidates for $R_{X}$ which can be calculated via $R_{X}=Q_{M_{A}}PQ_{M_{B}}^T$, and the corresponding $t_{X}$ can be obtained from Eq.\textcolor{blue}{~}(\ref{equ17b}). Given known $X$, $Y$  can be solved from $Y = M_AXM_B^{-1}$. At last, eight candidate pairs of  $\{X_{k},Y_{k}\}$ can be obtained as:

@@

The problem then becomes selecting the best pair of $\{X_k, Y_k\}$ from the eight candidates.
Based on screw theory, it is known that a homogeneous transformation $H$ can be expressed by the four screw parameters $(\theta,d,\mathbf{n},\mathbf{p})$ that define the $Pl\ddot{u}cker$ coordinates of the screw motion as:

@@

Moreover, $A X_k = Y_k B$ can be written as $AX_k=X_k(X_k^{-1}Y_kB)$. Defining $B^k = X_k^{-1}Y_kB$, we have $AX_k=X_kB^k$. There exist two Euclidean-group invariant relationships for each pair of $(A_{i},B_{i}^k)( i = 1,\cdots,n; k=1,\dots,8)$ as follows:

@@

\begin{equation}\label{equ23}
    (X,Y) = \mathop{\mathbf{arg}min}_{(X_{k},Y_{k})}\frac{1}{n} \sum_{i=1}^{n} (\parallel \theta_{A_{i}}-\theta_{B_{i}^{k}} \parallel + \parallel d_{A_{i}}-d_{B_{i}^{k}} \parallel)
\end{equation}
Eight candidates of $(X_k, Y_k)$ are calculated using the probabilistic method on $SE(3)$, which doesn't require the correspondence between $A_{i}$ and $B_{j}$ to be known. However, the correspondences need to be recovered to pick the optimal $(X_k, Y_k)$.
\section{Solution with unknown correspondence between $A_{i}$ and $B_{j}^{k}$}
\label{sect3}

In most cases, the two sets of homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors. Due to the asynchronous timing of the sensor readings, the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$ is usually unknown. This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and the Euclidean-group invariants are used to recover the correspondence between the data streams. The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is no a priori knowledge of the correspondence. However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-group invariants, it is straightforward to determine which is the optimal pair if the correspondence between $A_{i}$ and $B_{j}^{k}$ can be known.

@@

The discrete convolution of two sequences $f_{n}$ and $g_{n}$ is defined as:

\begin{equation}\label{equ26}
	(f \ast g)(\tau)=\sum_{j=0}^{N}f(t_{j})g(t_{j}-\tau).
	% Since you are using i for imaginary numbers use j here instead
    %(f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
\end{equation}

@@

\begin{equation}\label{equ28}
    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot \mathcal{F}^{*}(g)].
\end{equation}

Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the Fast Fourier Transform (FFT).
